---
title: "Simple document"
author: Maya Krishnamoorthy
date: 2024-09-10
output: github_document
---
```{r, echo=FALSE, message=FALSE}
library(tidyverse)
```

I loaded necessary packages (e.g. `tidyverse`).

I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3 - Learning Assessment

Here's a **code chunk** for the learning assessment (Sep 10). It creates `la_df` and then plots a histogram.
We can use option+cmd+i to create a new code chunk.

```{r la_chunk, message=FALSE}

la_df = tibble(
  vec_num = rnorm(500, mean=1),
  vec_log = vec_num>0,
  vec_abs = abs(vec_num)
)

# If we don't want code to show, make a new code chunk and don't evaluate (i.e. eval=FALSE, echo=FALSE)
ggplot(la_df, aes(x = vec_abs)) + geom_histogram()

```

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell